\documentclass[11pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\pagenumbering{gobble}

\begin{document}

\begin{center}
  {\Large \textbf{Aisha Rahman}}\\
  Kuala Lumpur, Malaysia \textbar{} +60 12-345 6789 \textbar{} \href{mailto:aisha.rahman@example.com}{aisha.rahman@example.com}\\
  \href{https://www.linkedin.com/in/aisha-rahman-example}{linkedin.com/in/aisha-rahman-example}
\end{center}

\section*{Professional Summary}
Junior software developer with experience building responsive web applications, integrating REST APIs, and collaborating in Agile teams. Comfortable with JavaScript, React, Node.js, SQL, Git, and automated testing.

\section*{Technical Skills}
\begin{itemize}[leftmargin=*,nosep]
  \item \textbf{Languages:} JavaScript, TypeScript, HTML, CSS, SQL, Python
  \item \textbf{Frameworks and tools:} React, Node.js, Express, PostgreSQL, Git, GitHub, Jest, Figma
  \item \textbf{Practices:} REST API integration, responsive design, Agile/Scrum, code review, unit testing
\end{itemize}

\section*{Experience}
\textbf{Software Development Intern} \hfill May 2025 -- Aug 2025\\
BrightPath Digital, Kuala Lumpur
\begin{itemize}[leftmargin=*,nosep]
  \item Built reusable React components for an internal customer-support dashboard used by 15 support staff.
  \item Integrated REST endpoints in a Node.js service and added input validation for customer records.
  \item Wrote unit tests with Jest and participated in weekly code reviews with a four-person development team.
  \item Collaborated with a designer to improve mobile layouts for the company website.
\end{itemize}

\section*{Projects}
\textbf{Job Application Tracker} \hfill 2025
\begin{itemize}[leftmargin=*,nosep]
  \item Created a React and Node.js application for tracking job applications, interview dates, and application statuses.
  \item Designed a PostgreSQL data model and implemented CRUD REST API endpoints.
  \item Used GitHub Issues to plan tasks and deployed the project for peer testing.
\end{itemize}

\textbf{Campus Events Portal} \hfill 2024
\begin{itemize}[leftmargin=*,nosep]
  \item Developed a responsive event listing interface with HTML, CSS, JavaScript, and Figma wireframes.
  \item Added search and category filters to help students find relevant campus events.
\end{itemize}

\section*{Education}
\textbf{Bachelor of Computer Science} \hfill Expected 2027\\
Example University, Kuala Lumpur

\end{document}
